D-Hammer: Efficient Equational Reasoning for Labelled Dirac Notation

### 2025-01-31 02language_design.tex
.

\gb{these two paragraphs do not make too much sense. We also need to define \( E \vdash e_1 = e_2 \)}The scalar theories are treated separately as a module and are not considered in this work. In the implementation, we use the Mathematica kernel to decide scalar equivalences.

@@

\subsection{Algorithm to Decide Equivalence}

>>>>

\gb{these two paragraphs do not make too much sense. We also need to define what is an equation and what is the meaning of \( E \vdash e_1 = e_2 \)}The scalar theories are treated separately as a module and are not considered in this work. In the implementation, we use the Mathematica kernel to decide scalar equivalences.

@@

\subsection{Algorithm to Decide Equivalence}
\gb{I still think that the names first rewritings, second rewriting and de bruijn normalization are not good, in particular, de bruijn normalization is non-standard terminology that will make people familiar with the field cringe.}
